Finding Groups Within the Data

### 2016-07-02 ab_tests/frequentist_ab_test.Rmd
data hygiene, increase rmarkdown font size

>>>>

<style type="text/css">
p{ /* Normal  */
   font-size: 18px;
}
body{ /* Normal  */
   font-size: 18px;
}
td {  /* Table  */
   font-size: 14px;
}
h1 { /* Header 1 */
 font-size: 32px;
}
h2 { /* Header 2 */
 font-size: 26px;
}
h3 { /* Header 3 */
 font-size: 22px;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre { /* Code block */
  font-size: 14px
}
</style>

### 2016-07-02 articles/articles.Rmd
data hygiene, increase rmarkdown font size

- Reddit and Facebook Veteran On How to Troubleshoot Troublemakers. [[First Round Review](http://firstround.com/review/reddit-and-facebook-veteran-on-how-to-troubleshoot-troublemakers/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
    - Hermits. Get them to collaborate with a team.
    - Nostalgia. Ask qualities that they missed most, and see if there're existing projects that could allow them to recapture that feeling.
    - Trend Chaser. Ask them why this is the route their going to take? The potential has to worth more than the expense of experimenting.
- Labels are for cans not for people. [[Facebook Videos](https://www.facebook.com/morokcom/videos/237500609921393/)]
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- Land any job you want. [[blog](http://landanyjobyouwant.com/)]
- The career advice no one tells you. [[Quartz](http://qz.com/640112/the-career-advice-no-one-tells-you/)]
- Wanted in College Graduates: Tolerance for Ambiguity. [[Linkedin Pulse](https://www.linkedin.com/pulse/wanted-college-graduates-tolerance-ambiguity-jeff-selingo)]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

>>>>

- 5 Qualities You Need to Show in the Job Search. [[glassdoor](https://www.glassdoor.com/blog/qualities-show-off/?utm_source=newsletter&utm_medium=email&utm_content=Top5Jobs_US16&utm_campaign=May2016_US)]
    - Leadership ability. e.g. As a result of an incentive program I spearheaded, our sales team surpassed its quarterly sales goal by 15 percent.
    - Flexibility: keep track of times when you’ve had to assume multiple roles or responsibilities outside of your own.
    - Coachability: Be open and honest about where you fall short and how you’re actively improving on those shortcomings.
- From Developer to Manager - PyCon 2016. [[Youtube](https://www.youtube.com/watch?v=lzBm0r8CxhY)]
- Reddit and Facebook Veteran On How to Troubleshoot Troublemakers. [[First Round Review](http://firstround.com/review/reddit-and-facebook-veteran-on-how-to-troubleshoot-troublemakers/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
    - Hermits. Get them to collaborate with a team.
    - Nostalgia. Ask qualities that they missed most, and see if there're existing projects that could allow them to recapture that feeling.
    - Trend Chaser. Ask them why this is the route their going to take? The potential has to worth more than the expense of experimenting.
- Labels are for cans not for people. [[Facebook Videos](https://www.facebook.com/morokcom/videos/237500609921393/)]
- Practical Frameworks for Beating Burnout [[First Round Review](http://firstround.com/review/practical-frameworks-for-beating-burnout/?ct=t(How_Does_Your_Leadership_Team_Rate_12_3_2015))]
- Land any job you want. [[blog](http://landanyjobyouwant.com/)]
- The career advice no one tells you. [[Quartz](http://qz.com/640112/the-career-advice-no-one-tells-you/)]
- Wanted in College Graduates: Tolerance for Ambiguity. [[Linkedin Pulse](https://www.linkedin.com/pulse/wanted-college-graduates-tolerance-ambiguity-jeff-selingo)]
- How to set goals: OKRs. [[Youtube](https://www.youtube.com/watch?v=mJB83EZtAjc)]
- Meetings that don’t suck. [[Youtube](https://www.youtube.com/watch?v=rU8nv38E0Qk)]

@@

- Check Yourself: 5 Things You Should Know About Data Science (Author Note). [[Blog](http://analyticsmadeskeezy.com/2012/11/05/check-yo-self-5-things-you-should-know-about-data-science-author-note/)]
- Statistics for Hackers - PyCon 2016 [[Youtube]](https://www.youtube.com/watch?v=-7I7MWTX0gA)
- The questions to ask before implementing any big data strategy. [[the guardian](http://www.theguardian.com/sap-partner-zone/2016/apr/28/questions-before-implementing-big-data-strategy)]
    - What is the biggest challenge my business is facing right now and what do you do and don't know about your customer. and see how you can tweak your current strategy to make it more customer and data-driven.

### 2016-07-02 finding_groups/finding_groups.Rmd
data hygiene, increase rmarkdown font size

---
title: "Business Analytics - Finding Groups Within the Data"
author: "Ming-Yu Liu"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: pygments
---

> This documentation assumes you're familiar with hierarchical clustering.

## Background Information

This documentation will go over two examples of how identifying groups within data allows business to improve efficiency. Finding groups within our data allows us to strike the right balance between similarities and differences. The reason behind this is we want to treat similar cases with similar appoaches to benefit from the economics of scale. On the other hand, treating different scenarios with different ways that are more suitable to the current situations will improve your actions' effectiveness. The following documentation will cover two examples of where this notion can be use in the business world.

## Example 1 : Supply Chain Management

@@

@@

## Example 2 : Humance Resources

@@

```{r, fig.height=8, fig.width=12 }

@@

## Takeaways

@@

**Sources:**

This wraps up our example of where clustering algorithms can be used to improve your businesses efficiency. You can find all the code (finding_groups.R) and datasets (in the data folder) used in this documentation [here](https://github.com/ethen8181/Business-Analytics/tree/master/finding_groups).

Any comments or suggestions is appreciated. That includes bugs or typos report. You can file these new issues [here](https://github.com/ethen8181/Business-Analytics/issues).

## R Session Information

>>>>

---
title: "Finding Groups Within the Data"
author: "Ming-Yu Liu"
date: "2016-04-05"
output:
  rmdformats::readthedown:
    highlight: pygments
---

<style type="text/css">
p{ /* Normal  */
   font-size: 18px;
}
body{ /* Normal  */
   font-size: 18px;
}
td {  /* Table  */
   font-size: 14px;
}
h1 { /* Header 1 */
 font-size: 32px;
}
h2 { /* Header 2 */
 font-size: 26px;
}
h3 { /* Header 3 */
 font-size: 22px;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre { /* Code block */
  font-size: 14px
}
</style>

> You can find all the code and datasets (in the data folder) used in this documentation [here](https://github.com/ethen8181/Business-Analytics/tree/master/finding_groups).This documentation assumes you're familiar with hierarchical clustering.

We will go over two examples of how identifying groups within data allows business to improve efficiency. Finding groups within our data allows us to strike the right balance between similarities and differences. The reason behind this is we want to treat similar cases with similar appoaches to benefit from the economics of scale. On the other hand, treating different scenarios with different ways that are more suitable to the current situations will improve your actions' effectiveness. The following documentation will cover two examples of where this notion can be use in the business world.

# Example 1: Supply Chain Management

@@

```{r, message=TRUE, warning=TRUE}

@@

# Example2 : Humance Resources

@@

```{r, fig.height=8, fig.width=12, message=FALSE, warning=FALSE}

@@

**Takeaways**

@@

# R Session Information
